---
title: "Descriptive Statistics"
page-navigation: false
format:
  html: 
    toc: false
---

```{r, echo = FALSE, include = FALSE}
source(here::here("R", "buttons.R"))
```

Welcome to the *Descriptive Statistics* module! In this module, you will learn about: 

1. [Summarizing data](/tutorials/summarizing-data-baseR/index.qmd): How to calculate summary statistics for numeric data
1. [Frequency tables](/tutorials/frequency-tables-baseR/index.qmd): How to summarize categorical data


Each tutorial will comprise a series of interactive lessons with practice problems embedded throughout.

## Learning Goals

After completing this module, you will be able to:

### Summarizing Data

1. Calculate the mean, the standard deviation and the range of a variable
1. Create summary statistics using the summary() function
1. Use the describe() function
1. Account for missing values in your data when calculating summary statistics

### Frequency Tables

1. Make frequency tables in R
1. Make proportion and cumulative proportion tables
1. Make readable tables including various frequency measures
1. Making cross tables between two variables

Click the button below to get started with the first tutorial.

```{r}
#| echo: false
#| results: asis
begin_button("/tutorials/frequency-tables-baseR/index.html")
```
