---
title: "Descriptive Statistics"
page-navigation: false
format:
  html: 
    toc: false
---

```{r, echo = FALSE, include = FALSE}
source(here::here("R", "buttons.R"))
```

Welcome to the *Descriptive Statistics* module! In this module, you will learn about: 

1. [Frequency tables](/tutorials/frequency-tables-baseR/index.qmd)
1. [Summarizing data](/tutorials/summarizing-data-baseR/index.qmd) 

Each tutorial will comprise a series of interactive lessons with practice problems embedded throughout. Each tutorial section is wrapped up with a knowledge quiz.

## Learning Goals

After completing this module, you will be able to:

### Frequency Tables - Base R

1. A thing you should learn from Tutorial 2.
1. Another thing you should learn from Tutorial 2.

### Summarizing Data - Base R

1. Load, inspect, structure ( head, str), summary of all (summary())
1. Summary statistics: mean, median, var, sd, min, max, range
1. Apply over all numeric columns, sapply
1. Accounting for missing values in your data (na.rm)

Click the button below to get started with the first tutorial.

```{r}
#| echo: false
#| results: asis
begin_button("/tutorials/frequency-tables-baseR/index.html")
```
