---
title: "Descriptive Statistics"
page-navigation: false
format:
  html: 
    toc: false
---

```{r, echo = FALSE, include = FALSE}
source(here::here("R", "buttons.R"))
```

Welcome to the *Descriptive Statistics* module! In this module, you will learn about: 

1. [Summarizing data](/tutorials/summarizing-data-baseR/index.qmd): How to calculate summary statistics for numeric data
2. [Frequency tables](/tutorials/frequency-tables-baseR/index.qmd): How to summarize categorical data
3. [Summarizing data with tidyverse](/tutorials/summarizing-data-tidy/index.qmd): How to calculate summary statistics for numeric data using the tidyverse
4. [Frequency tables with tidyverse](/tutorials/frequency-tables-tidy/index.qmd): How to summarize categorical data using the tidyverse
5. [pivoting tables](/tutorials/pivots/index.qmd): How to reshape and summarize data 


Each tutorial will comprise a series of interactive lessons with practice problems embedded throughout.

## Learning Goals

After completing this module, you will be able to:

### Summarizing Data

1. Calculate the mean, the standard deviation and the range of a variable
1. Create summary statistics using the `summary()` function
1. Use the `describe()` function
1. Account for missing values in your data when calculating summary statistics

### Frequency Tables

1. Make frequency tables in `R`
1. Make proportion and cumulative proportion tables
1. Make readable tables including various frequency measures
1. Making cross tables between two variables

### Summarizing Data with the Tidyverse

1. Use `summarise()` to compute descriptive statistics in a tidy, pipeline-based workflow
2. Apply summary functions to multiple variables at once using `across()`
3. Create grouped summaries with `group_by()`
4. Compute counts, proportions, and missingness with tidyverse tools

### Frequency Tables with the Tidyverse

1. Use `count()` to generate tidy frequency tables
2. Add proportions and cumulative proportions using `mutate()`
3. Create grouped or conditional frequency tables

Pivoting and Reshaping Data

1. Understand when long or wide format is most appropriate for descriptive analyses
2. Use `pivot_longer()` to transform repeated measures into tidy long format
3. Use `pivot_wider()` to restructure summaries or prepare matrix-like data
4. Control naming conventions and handle missing values during pivoting

Click the button below to get started with the first tutorial.

```{r}
#| echo: false
#| results: asis
begin_button("/tutorials/summarizing-data-baseR/index.html")
```
