---
title: "From Long to Wide"
---

```{r, echo=FALSE}
library(dplyr)
library(tidyr)
data("bfi", package = "psych")
bfi_small_long <- bfi %>% 
  mutate(id = row_number()) %>%
  select(id, A1, A2, A3) %>%
  pivot_longer(
    cols = A1:A3,
    names_to = "item",
    values_to = "response"
  )
```


Sometimes we need to reverse the transformation.
Imagine we start from a long dataset like the one above and want to restore the original columns—this time using `pivot_wider()`:

```{r}
library(dplyr)
library(tidyr)
bfi_small_wide <- bfi_small_long %>%
  pivot_wider(
    names_from = item,
    values_from = response
  )
```

The resulting dataset has one row per participant (id) and separate columns for A1, A2, and A3 again.
`pivot_wider()` is especially useful when creating summary tables or preparing data for export.

## Dealing with Missing Values

Pivoting can introduce missing values when not every subject has measurements in every category.
`pivot_wider()` gives you a simple way to fill missing cells with a chosen value:

```{r}
bfi_small_long %>%
  pivot_wider(
    names_from = item,
    values_from = response,
    values_fill = 0     # or NA, or any other placeholder
  )

```

This is useful for preparing matrices for models or visualizations that require complete grids.

```{webr-r}
#| autorun: true
#| context: setup
library(tibble)
long_data <- tibble(
  id = c(1, 1, 2, 3, 3, 3),
  variable = c("X", "Y", "X", "X", "Y", "Z"),
  value = c(10, 20, 30, 40, 50, 60)
)
library(dplyr)
library(tidyr)
```

::: practice

## Practice

Transform the this long dataset back to wide format using `pivot_wider()`, ensuring that missing values are filled with -1.

```{r, echo=FALSE}
library(tibble)
long_data <- tibble(
  id = c(1, 1, 2, 3, 3, 3),
  variable = c("X", "Y", "X", "X", "Y", "Z"),
  value = c(10, 20, 30, 40, 50, 60)
)
head(long_data)
```


:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}

```

## {{< var tab_title.solution >}}

```{r}
long_data %>%
  pivot_wider(
    names_from = variable,
    values_from = value,
    values_fill = -1
  )
```
::::

:::



