---
title: "Making Readable Tables"
---

```{r, echo = FALSE}
songs <- read.csv2(here::here("data", "songs.csv"),header=TRUE, sep=",")
```

We have now retrieved various tables (frequencies, proportions, percentages, and the cumulative sum), and we can extract the information we need from them, but they are not very readable. 

We can also combine these different options in R into a single table. We will do this for the variable `THEME`. 
To do this, we first create all the separate tables and give them clear names:

```{r}
frequencies <- table(songs$THEME, exclude = NULL)
proportions <- prop.table(frequencies)
cum_proportions <- cumsum(proportions)
percentages <- prop.table(frequencies)*100
cum_percentages <- cumsum(percentages)
```

Then we can combine these tables using the `cbind()` function. This ensures that each separate table fills one column in the combined table. 

```{r}
cbind(frequencies, percentages, cum_percentages, proportions, cum_proportions)
```

Now we have everything clearly arranged side by side!