---
title: "Frequency tables"
---

```{r, echo = FALSE}
songs <- read.csv2(here::here("data", "songs.csv"),header=TRUE, sep=",")
```

The tidyverse provides the `count()` function, a clean and expressive way to produce frequency tables. It takes a data frame and a variable, and returns a tibble with the variable’s values and their frequencies.

```{r}
library(dplyr)
songs %>% count(THEME)
```

This gives a simple table with two columns:

- the category (e.g., levels of education)
- the number of cases in each category

If you want the categories sorted from most to least frequent, you can add:

```{r}
songs %>% count(THEME, sort = TRUE)
```

This replaces `sort(table(x))` with a single tidy and readable expression.

```{webr-r}
#| autorun: true
#| context: setup
download.file("https://openstatprog.com/raw-data/songs.csv", "songs.csv")
songs <- read.csv("songs.csv")
library(dplyr)
```

::: practice

## Practice

Make a frequency table for the variable `YEAR` with `dplyr`. 

*NOTE:* The `songs` dataset and the `dplyr` package are already loaded in the working directory of this *webr* session.

:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}

```

## {{< var tab_title.solution >}}

```{r}
songs %>% count(YEAR)
```
::::

:::