---
title: "Code Blocks"
---

This is the first topic file for Tutorial 1.

- Such topic files should cover one substantively meaningful chunk of content.

## Code Blocks

Use **knitr** code blocks to include non-interactive R code.

```{r}
## Add 2 and 2
2 + 2

## Divide 225 by 15 and print the result
(x <- 225 / 15)
```

Use **quarto-webr** code blocks for interactive R exercises.

```{webr-r}
fit <- lm(Petal.Length ~ Petal.Width, data = iris)
summary(fit)
```

### Code Block Environments

A single execution environment is shared across code blocks of the same type.

- All the **knitr** code blocks in a QMD file will share an evaluation environment.
- Likewise for the **quarto-webr** code blocks

```{r}
x^2
```

```{webr-r}
confint(fit)
```

**knitr** and **quarto-webr** code blocks to not share the same environment, though.

```{r, error = TRUE}
resid(fit)
```

```{webr-r}
sqrt(x)
```

If you want to share objects across code chunk types (e.g., to pose a practice problem using objects created in a
**knitr** chunk), you can regenerate the required objects using a hidden code chunk of the appropriate type.

- Don't forget to set an appropriate seed, if you're trying to regenerate a stochastic object.

### Inline Code

Use **knitr** inline code chunks to embed R output in text blocks.

- E.g., R says the squareroot of 2 is `r sqrt(2)`.
