---
title: "Basic Summaries"
---

```{r, echo = FALSE}
stocks <- read.csv(here::here("data", "stocks.csv"), header = TRUE, sep = ",", dec = ".", na.string = c("", "NA"))
```

The heart of tidyverse descriptive statistics is the `summarise()` function. It reduces a dataset to one or more summary statistics.

Suppose we want to compute the mean, minimum, and maximum of the `YEAR` variable in the stock data:

```{r}
library(dplyr)
stocks %>%
  summarise(
    mean_year = mean(YEAR, na.rm = TRUE),
    min_year  = min(YEAR,  na.rm = TRUE),
    max_year  = max(YEAR,  na.rm = TRUE)
  )

```

This code produces a one-row tibble containing the requested values.

Notice that we must explicitly set `na.rm = TRUE`. Unlike base R’s `summary()`, tidyverse functions never remove missing values unless told to do so. This makes missing-data handling visible and intentional.

```{webr-r}
#| autorun: true
#| context: setup
download.file("https://openstatprog.com/raw-data/stocks.csv", "stocks.csv")
stocks <- read.csv("stocks.csv")
library(dplyr)
```


::: practice

## Practice

Try requesting the mean of `SPSTOCKS` from the `Stocks` dataset using `dplyr`. 

*NOTE:* The `songs` dataset and the `dplyr` package are already loaded in the working directory of this *webr* session.

:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}

```

## {{< var tab_title.solution >}}

```{r}
stocks %>%
  summarise(
    mean_spstocks = mean(SPSTOCK, na.rm = TRUE)
  )
```
::::

:::





