Question
========
```{r, echo = FALSE, include = FALSE}
library(printr)
```

Use the following help file excerpt to answer the question below.

```{r, echo = FALSE, printr.help.sections = "usage"}
?cor
```
What is the default value for the `use` argument of the `cor()` function?

Answerlist
----------
* `"everything"`
* `"Everything`
* `"spearman"`
* `"pearson"`
* `"kendall"`
* `c("pearson", "spearman", "kendall")`
* `NULL`
* `method`
* `y`
* `x`
* The `use` argument does not have a defined default value.

Solution
========
The default value for the `use` argument is `"everything"`.

Answerlist
----------
* Correct
* Wrong: The "E" should be lowercase
* Wrong: This is one of the possible methods
* Wrong: This is one of the possible methods
* Wrong: This is one of the possible methods
* Wrong: These are all of the possible methods
* Wrong: This is the default value for `y`
* Wrong: This is an argument name
* Wrong: This is an argument name
* Wrong: This is an argument name
* Wrong: There is a default value defined for `use`.

Meta-information
================
exname: Default Arguments Selection
extype: schoice
exsolution: 10000000000
exshuffle: 5
