---
title: "Calculating summary statistics of variables"
---

```{r, echo = FALSE}
stocks <- read.csv(here::here("data", "stocks.csv"), header = TRUE, sep = ",", dec = ".", na.string = c("", "NA"))
```

The examples in this lesson are based on a data set about profits from stocks and bonds. We can take a look at the data using `head()`, which shows us the first 6 rows of the data frame.

```{r}
head(stocks)
```

The data set contains five variables. For which we provide some extra information here: 

-   **YEAR**: the year
-   **TBONDS**: Price of Treasury Bonds, US government bonds. For example, a figure of 4 means an increase of 4%.
-   **SPSTOCKS**: S&P 500 Stocks price, shares of the 500 largest US companies. For example, a figure of 44 means an increase of 44%.
-   **TBONDS_D**: Indicates whether Treasury Bonds rose (1) or fell/remained the same (0) that year.
-   **SPSTOCKS_D**: Indicates whether the S&P 500 stocks rose (1) or fell/remained the same (0) that year.

The `str()` function tells us what the class of each variable is. You will notice that most variables in the stocks data contain integers.

```{r}
str(stocks)
```

We will explore this data set further. At the start, we are interested to get more information about our collected variables. In most cases, we want at least to know the following parameters:

-   the mean
-   the standard deviation
-   the range (minimum and maximum)

For this purpose, `R` provides the following functions: 

```{r, eval= FALSE}
mean()
sd()
min()
max()
```

You can use these for a single variable (at a time). You can call up each variable by adding `$‘variable name’` after the name of the data frame.

::: practice

## Practice

Try requesting the mean of SPSTOCKS from the Stocks dataset. 

:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}

```

## {{< var tab_title.solution >}}

```{r}
mean(stocks$SPSTOCKS)
```
::::

:::
