---
title: "The summary function"
---

```{r, echo = FALSE}
stocks <- read.csv(here::here("data", "stocks.csv"), header = TRUE, sep = ",", dec = ".", na.string = c("", "NA"))
```

We can produce several of these summary statistics at once by using the `summary()` command from ‘base R’ (i.e. without installing packages). You can use this on your entire dataset at once. 

::: practice

## Practice

Try requesting the summary statistics for the entire stocks dataset. 

:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}

```

## {{< var tab_title.solution >}}

```{r}
summary(stocks)
```
::::

:::

If you want to retrieve descriptive statistics for multiple variables, you can use the entire data frame as an argument for `summary()`. You can also select a subset of variables (columns) by using, for example, `stocks[1:3]` as an argument to select the first three columns or `stocks[c(1,2,4)]` to select column 1, 2 and 4. Try it out!

::: practice

## Practice

Try requesting the summary statistics for column 2 and 5 of stocks. 

:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}

```

## {{< var tab_title.solution >}}

```{r}
summary(stocks[c(1,5)])
```
::::
:::


